---
title: "Weight of Fish"
author: "Fernando D Velasquez"
date: "April 27, 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

```{r}
FishData=read.csv(file="Fish.csv")
```


# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  

# Perch

## Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

```{r}
PerchData= filter(FishData,Species=="Perch")
PerchData = subset (PerchData, select = -Species)
```


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = PerchData,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
### Which is best??  

The best model uses two variables which are Heigth and Width.  

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[3,]
```

```{r}
best.model <- lm(Weight~ Height + Width,data=PerchData)
fullup <- lm(Weight~.,data=PerchData)
summary(best.model)
```
The P-Value is so small making this model excellent.  

```{r}
anova(fullup,best.model)
```


# Bream

## Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

```{r}
BreamData= filter(FishData,Species=="Bream")
BreamData = subset (BreamData, select = -Species)
```


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = BreamData,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
### Which is best??

The best model uses length2,length3,width, and height.  


```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[3,]
```

```{r}
best.model <- lm(Weight~ Length2 + Height ,data=BreamData)
fullup <- lm(Weight~.,data=BreamData)
summary(best.model)
```
  
The P Value for Bream is small making this model a good fit.

```{r}
anova(fullup,best.model)
```
P Value is too big to use 3 variables so 2 variables fit well.  

# Smelt

## Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->


```{r}
SmeltData= filter(FishData,Species=="Smelt")
SmeltData = subset (SmeltData, select = -Species)
```



## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = SmeltData,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
### Which is best??  

The best model uses Length1,Length2, width and height.  


```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[3,]
```

```{r}
best.model <- lm(Weight~ Length2 + Width,data=SmeltData)
fullup <- lm(Weight~.,data=SmeltData)
summary(best.model)
```
P Value is small enough making this model an excellent fit.  

```{r}
anova(fullup,best.model)
```
The p value is big enough making this model a better fit.   

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

In conclusion, we determined that their is no difference in using a model with 2 or more variables. We can concluded this by looking at the r squares and p values. The P values were so small that it benefits all 3 models of fish population. We reject the null hypothesis as the anovas were large which we can say that their is no differences between using a model with 2 or more variables.  


